---
title: "Lab 8: The 12 Days of Christmas"
author: "Nithya Chandran, Athena Kwok, Catherine Phan, Christina Dang, Ye Chan Yoo"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Packages for Functions
library(dplyr)
library(glue)
library(stringr)
library(purrr)
library(english)
```


### A Test Dataset

```{r}
xmas <- read.csv("https://www.dropbox.com/s/e584pryn8evm1gz/xmas.csv?dl=1")
```

---

## Step One:  Plurals

Note that the gifts are listed in singular: for example, on day five the
narrator receives "five golden rings", but the entry in the dataset for the gift
on day 5 simply says "ring".  

Using the skeleton of the `pluralize_gift()` function, complete the code so that 
the function takes a gift and returns the appropriate plural. 

```{r}
# Function that takes a noun and makes it plural
# Arguments -- gift -- A string or vector of strings
# Return -- A string or vector of strings with the pluralized words

pluralize_gift <- function(gift){

gift <- gift %>%
  paste0("s") %>%
  str_replace("ys$", "ies") %>%
  str_replace("ooses$", "eese")

return(gift)

}
```

- The [`paste0()` function](https://stackoverflow.com/questions/28028110/insert-character-at-end-of-string-in-r-except-for-the-last-element) works similar to `paste()` but the default `sep` is an empty string (`""`) in `paste0()` and the default `sep` is a single space (`" "`) in `paste()`.



### Test Your Function

Try your function out on the gifts in the dataset.  
(Consider: is your function *vectorized*?  It does not have to be, but it may
make things simpler!)

```{r}

pluralize_gift(xmas$Gift.Item)

purrr::map_chr(xmas$Gift.Item, pluralize_gift)

```


---


## Step Two: Creating sentences


```{r}
make_phrase <- function(num, num_word, item, verb, adjective, location) {
  
  ## Step 1: Replace NAs with blank strings
  verb <- str_replace_na(verb, "")
  adjective <- str_replace_na(adjective, "")
  location <- str_replace_na(location, "")
  
  ## Step 2: Pluralize the gift if needed
  ## Items with numbers larger than 1 should be pluralized
  ## Single items starting with a vowel should have "an" in front
  ## All other single items should have "a" in front
  
  vowel_start <- str_sub(item, 1, 1) %>% str_detect("[aeiou]")
  
  if (num > 1) {
    
    item <- pluralize_gift(item)
    
  } else if (vowel_start) {
    
    num_word <- "an "
    
  } else {
    
    num_word <- "a "
    
  }
  
  glue::glue("{num_word} {adjective} {item} {verb} {location}") %>%
    str_squish()
  
  
}
```


# Test Your Function

Try your function out on the `xmas` data, by making a new variable containing
the daily phrases.

**Hint:** The `Day.in.Words` variable isn't quite what you want! You want `12`
to say `"twelve"` **not** `"twelfth"`. I suggest using the **english** package
to create numbered days and then use those in your `pmap_chr()`!

```{r}
xmas <- xmas %>%
  mutate(
    days_in_words = as.character(english::english(Day)),
    Full.Phrase = pmap_chr(list(Day, days_in_words, Gift.Item, Verb, Adjective, Location), 
                           make_phrase)
  )
```

---


## Step Three:  Iteration.

Write a function called `sing_line` that takes as input:

* A dataset

* A number indicating which day to sing about

* The name of a column in the dataset that contains the phrases for each day.

```{r}
# Produces the string for one day of the song.
# Arguments -- dataset -- A data frame containing information about gifts
# Arguments -- line -- The number of the line for the day you want to sing about
# Arguments -- phrase_col -- The variable name for the column in the dataset that contains the gift phrases
# Return -- A string singing the line of the song with all gifts for the given day.

sing_line <- function(dataset, line, phrase_col){
  
  # Step 1: Setup the intro line
  
  num_word <- english::ordinal(line)
  
  intro <- glue::glue("On the {num_word} day of Christmas, my true love sent to me,")
  
  # Step 2: Sing the gift phrases

  phrases <- dataset %>% 
    pull({{phrase_col}})
  
  if(line > 1){
    phrases[2] <- paste0(phrases[2], " and")
  }

  gift_phrases <- str_c(phrases[line:1], collapse = "\n")
    
  ## put it together
    
  glue::glue("{intro} \n{gift_phrases}")


}


```

- [ordinal() function from english package](https://rdrr.io/cran/english/man/ordinal.html) The `ordinal()` function takes a number and return the ordinal number. For example, `ordinal(2)` will return `second`.

For example,


```{r}
sing_line(xmas, 
          line = 2, 
          phrase_col = Full.Phrase)

```

should return

```
On the second day of Christmas, my true love sent to me,
two turtle doves 
and a partridge in a pear tree.
```

*Hint:*  The `{{phrase_col}}` part, which I provided for you, lets you use 
column names as arguments to a function.  Don't delete that line of code!

---

## Step Four: Use Your Functions!

Run the following code to test out your functions! The ouput should be the 
lyrics for the entire 12 Days of Christmas song. 
```{r}
xmas2 <- xmas %>%
  mutate(
    day.num = as.character(english::english(Day)), 
    Full.Phrase = pmap_chr(list(num = Day, 
                                num_word = day.num, 
                                item = Gift.Item, 
                                verb = Verb, 
                                adjective = Adjective, 
                                location = Location), 
                           make_phrase)
  )

map_chr(1:12, ~sing_line(xmas2, .x, Full.Phrase)) %>%
  str_c(collapse = "\n") %>%
  cat()

```

## Step Five: Show Me Your Work! 

#### Get it on GitHub

Once you are done with all the functions, make sure you have **pushed** your
work to GitHub.

Make sure your repository contains your completed RMarkdown document and
knitted HTML. 

- Your HTML should **only** show the code for your functions and output from 
testing / verifying that your functions perform as they should. 

__If you used GitHub to store your work:__

Submit the link to your GitHub repository in the Lab 8 assignment portal. 

__If you downloaded the compressed folder and did not use GitHub:__

Submit **both** your RMarkdown file and knitted HTML file